

\cvsection{Projects}

\begin{cventries}
  \cventry
    {Bioinformatics}
    {Integrated Omics Pipeline for Microbial Genomics}
    {}
    {}
    {
      \begin{cvitems}
        \item {Developed a comprehensive pipeline integrating metagenomic, transcriptomic, and proteomic data for functional gene analysis and microbial community profiling.}
      \end{cvitems}
    }
  \cventry
    {Bioinformatics}
    {Single-Cell \& Spatial Transcriptomics Workflow}
    {}
    {}
    {
      \begin{cvitems}
        \item {Implemented analysis workflows for single-cell RNA-seq and spatial transcriptomics data, enabling cell type identification and trajectory inference.}
      \end{cvitems}
    }
  \cventry
    {Biotechnology}
    {Bioprocess Optimization for Protein Production}
    {}
    {}
    {
      \begin{cvitems}
        \item {Optimized fed-batch fermentation processes for heterologous protein expression in Pichia pastoris, including pathway engineering and bioreactor management.}
      \end{cvitems}
    }
  \cventry
    {Programming}
    {Automation \& Web Data Extraction Solutions}
    {}
    {}
    {
      \begin{cvitems}
        \item {Designed and deployed Python-based web crawlers and automation scripts for data extraction, cleaning, and processing from diverse online sources.}
      \end{cvitems}
    }
  \cventry
    {Programming}
    {Full-Stack Web Application for Data Visualization}
    {}
    {}
    {
      \begin{cvitems}
        \item {Built interactive dashboards and visualization tools using Django, React, and Plotly for scientific data representation and reporting.}
      \end{cvitems}
    }
  \cventry
    {Programming {\textbar} Bioinformatics}
    {Machine Learning Applications in Bioinformatics}
    {}
    {}
    {
      \begin{cvitems}
        \item {Developed predictive models and clustering algorithms for biological data analysis, focusing on gene expression and classification tasks.}
      \end{cvitems}
    }
  \cventry
    {Bioinformatics}
    {Containerized Bioinformatics Workflows}
    {}
    {}
    {
      \begin{cvitems}
        \item {Deployed reproducible bioinformatics pipelines using Docker and Kubernetes for scalable and collaborative research environments.}
      \end{cvitems}
    }
  \cventry
    {Programming}
    {CI/CD Pipeline Implementation for Web Applications}
    {}
    {}
    {
      \begin{cvitems}
        \item {Configured and automated continuous integration and deployment pipelines using GitLab CI/CD and Docker for web applications, ensuring robust delivery workflows.}
      \end{cvitems}
    }
  \cventry
    {Programming}
    {Backend API Development for Data-Driven Applications}
    {}
    {}
    {
      \begin{cvitems}
        \item {Designed RESTful APIs with Django Rest Framework and FastAPI to serve as backends for data-driven applications, focusing on performance and scalability.}
      \end{cvitems}
    }
  \cventry
    {Programming {\textbar} Bioinformatics {\textbar} Biotechnology}
    {Real-Time Data Visualization Dashboard}
    {}
    {}
    {
      \begin{cvitems}
        \item {Developed a real-time dashboard for monitoring and visualizing streaming data using React, WebSockets, and Plotly for interactive user experience.}
      \end{cvitems}
    }
  \cventry
    {Programming}
    {Full-Stack E-commerce Web Platform}
    {}
    {}
    {
      \begin{cvitems}
        \item {Built a scalable e-commerce platform integrating user management, product catalogs, and payment systems using Django, React, and PostgreSQL.}
      \end{cvitems}
    }
  \cventry
    {Programming {\textbar} Bioinformatics}
    {Linux System Automation \& Monitoring Scripts}
    {}
    {}
    {
      \begin{cvitems}
        \item {Created Bash and Python scripts for automating server maintenance tasks, log management, and resource monitoring on Linux-based systems.}
      \end{cvitems}
    }
  \cventry
    {Programming}
    {Cloud-Based Microservices Deployment}
    {}
    {}
    {
      \begin{cvitems}
        \item {Implemented microservices architecture and deployed containerized services on cloud infrastructure using Docker and Kubernetes.}
      \end{cvitems}
    }
  \cventry
    {Robotics {\textbar} Embedded Systems {\textbar} Student Projects}
    {Robotics \& Embedded Systems Developer — High School \& Personal Projects (2011–2015)}
    {}
    {}
    {
      \begin{cvitems}
        \item {Microcontroller programming and robot development for student competitions; designed and built embedded robotics systems and control logic.}
      \end{cvitems}
    }
  \cventry
    {Programming}
    {Policy Compliance Checker (Flask + React + SQLite)}
    {}
    {}
    {
      \begin{cvitems}
        \item {Built a FReMP stack web application to upload dynamic security policies and user datasets (JSON/CSV), evaluate per-user compliance server-side, and present filterable/exportable pass/fail results with explanations in a React UI.}
      \end{cvitems}
    }
\end{cventries}
